---
title: "HW1"
author: "Sarper Karabağ"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part 1 - EVDS Data Graph

```{r , echo=FALSE,warning=FALSE,message=FALSE}
library(tidyverse)
library(lubridate)
library(zoo)


d <- read.csv("EVDS2.csv")

#glimpse(d)

#(TP.DK.USD.A.YTL, TP.KTF10, Tarih, TP.HKFE01) 

d$Tarih <- as.yearmon(d$Tarih)

#glimpse(d)

ggplot(d, aes(x=Tarih)) + 
  geom_line(aes(y=TP.DK.USD.A.YTL, col="US Dollar")) + 
  geom_line(aes(y=TP.KTF10, col="Weighted Average Interest Rates For Banks Loans - Personal")) + 
  geom_line(aes(y=TP.HKFE01, col="Residential Property Price Index (RPPI)")) +
  labs(y=NULL) +
  theme_bw() +
  theme(legend.position="top" , legend.background = element_rect(fill="gray", linetype="solid"))


```

## Questions about the graph

### 1) Is there an increasing/decreasing trend?

In the last quarter of 2018, we can see that there is an one increasing as the others increase trend. Another observation from the graph that in late 2019 there is a 
decreasing trend on Weighted Average Interest Rates for Bank Loans while Residential 
Price Index.

### 2) Is there a quarterly or monthly similarity over the years?

In the last quarter of 2018 and first quarter of the2019

In late quarter of 2018 and in the late quarter of 2020.

### 3) Are there any abnormal observations?

In the late quarter of 2019 to early stages of 2020, we can observe an abnormality as normally 3 data behave similarly. 

### 4) What may be the reason of the behavior you observed?

One reason might be the increase in the rent rates in the 2019 as %18,27.

# Part2 - Google Trend Data Visualization

## Key word: Konut Kredisi

### US Dollar - Konut Kredisi


```{r , echo=FALSE,warning=FALSE,message=FALSE}
library(tidyverse)
library(lubridate)
library(zoo)

d <- read.csv("EVDS2.csv")


d$Tarih <- as.yearmon(d$Tarih)

konutkredisi <- read.csv("konutkredisi.csv")

konutkredisi$Tarih <- as.yearmon(konutkredisi$Tarih)

df <- left_join(d, konutkredisi, by = "Tarih")

ggplot(df, aes(x=Tarih)) + 
    geom_line(aes(y=konutkredisi, col="Konut Kredisi")) +
    geom_line(aes(y=TP.DK.USD.A.YTL, col="US Dollar"))+ 
    labs(y=NULL) +
    theme_bw() +
    theme(legend.position="top" , legend.background = element_rect(fill="gray", linetype="solid"))
    
    
```

 We can say that there is an increasing trend. When dollar price increases, mortgage increases. It can be observed after the first quarter of 2018.


### Weighted Average Interest Rates For Banks Loans(Personal) - Konut Kredisi


```{r , echo=FALSE,warning=FALSE,message=FALSE}
library(tidyverse)
library(lubridate)
library(zoo)

d <- read.csv("EVDS2.csv")


d$Tarih <- as.yearmon(d$Tarih)

konutkredisi <- read.csv("konutkredisi.csv")

konutkredisi$Tarih <- as.yearmon(konutkredisi$Tarih)

df <- left_join(d, konutkredisi, by = "Tarih")
ggplot(df, aes(x=Tarih)) + 
    geom_line(aes(y=konutkredisi, col="Konut Kredisi")) +
    geom_line(aes(y=TP.KTF10, col="Weighted Average Interest Rates For Banks Loans - Personal")) +
    labs(y=NULL) +
    theme_bw() +
    theme(legend.position="top" , legend.background = element_rect(fill="gray", linetype="solid"))

```

We can say that there is no certain trend but components are tend to behave opposite.

### Residential Property Price Index (RPPI) - Konut Kredisi

    
```{r , echo=FALSE,warning=FALSE,message=FALSE}
library(tidyverse)
library(lubridate)
library(zoo)

d <- read.csv("EVDS2.csv")


d$Tarih <- as.yearmon(d$Tarih)

konutkredisi <- read.csv("konutkredisi.csv")

konutkredisi$Tarih <- as.yearmon(konutkredisi$Tarih)
    
ggplot(df, aes(x=Tarih)) + 
    geom_line(aes(y=konutkredisi, col="Konut Kredisi")) +
    geom_line(aes(y=TP.HKFE01, col="Residential Property Price Index (RPPI)")) +
    labs(y=NULL) +
    theme_bw() +
    theme(legend.position="top" , legend.background = element_rect(fill="gray", linetype="solid"))
    
```

We can say that sudden increase in the mortgage, decreases the Residential Property Price Index. Hence, they behave opposite to the sudden changes.
